% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{resumeclass} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it Achuthananda MP}\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page

\begin{document}
\thispagestyle{empty} % this page has no header  
\name{ACHUTHANANDA MP\\[12pt]}% the \\[12pt] adds a blank line after name

\address{{\bf Profile}
  \\ http://myprofile.achuth.tech/
  \\ https://github.com/Achuthananda 
  \\ https://www.linkedin.com/in/achutha-nanda-a9694b37
  \\ {\bf Email} : achuthadivine@gmail.com
}
\address{{\bf Address} \\ Achu Priya Nilaya \\ 8th cross Jayanagar B-Block,\\ Kolar - 563101 \\ +919986014033}


\begin{resume}
 
\section{\centerline{EDUCATION}} 
\vspace{8pt} 
{\sl Master of Technology}, Information Technology \hspace{0.2in} \\
\textbf{IIT Kharagpur}  \hfill July 2014-May 2016\\
 
{\sl Bachelor of Engineering}, Information Science \hspace{0.2in}  \\ % \sl will be bold 
\textbf{Peoples Education Society Institute of Technology}, Bangalore     \hfill    Sep 2006-June 2010 \\

{\sl Pre University Course }, PCMB Combination \hspace{0.2in} \\ % \sl will be bold 
\textbf{Govt Boys Junior College}, Kolar  \hfill    June 2004- May 2006 \\

{\sl Secondary School } \hspace{0.2in} \\ % \sl will be bold 
\textbf{Mahila Samaja High School}, Kolar      \hfill    -May 2004 \\
 
\vspace{0.1in}
\section{\centerline{PROFILE SUMMARY}}
\vspace{15pt}
\begin{itemize}
\item 9 years 4 months of experience in Software Development,Design and Consulting.
\item Exposure to Analysis, Design, Implementation and Testing phases of Software development.
\item Expertise in Architecting CDN Solutions to improve Web Performance,Application Security Posture and Media Streaming Delivery.
\item Good understanding of Live and VOD Streaming Technologies.
\item Experience in DevOps, DevSecOps, Building CI/CD Pipelines, CLIs and Python SDKs.
\item Good understanding of Multi Cloud Setups such as Azure, AWS and GCP.
\item Expertise in DNS, HTTP, HTTPS, SAML, TCP/IP, DLNA, UPnP Protocols.
\item Expertise in Application and Middleware Development in various platforms such as Linux, Tizen, \& Android.
\item Good understanding of SDN and it's applications.


\end{itemize} 

\vspace{0.1in} 
\section{\centerline{PUBLICATIONS}} 
\vspace{15pt}
\begin{itemize}
  \item Misra, S., Bera, S., \textbf{Achuthananda, M. P.}, Pal, S. K., Obaidat, M. S. (2017). Situation-Aware
  Protocol Switching in Software-Defined Wireless Sensor Network Systems. IEEE Systems Journal.
  \item Misra, S., Wolfinger, B. E., \textbf{Achuthananda, M. P.}, Chakraborty, T., Das, S. N., Das, S. (2019). 
  Auction-based optimal task offloading in Mobile cloud computing. IEEE Systems Journal
\end{itemize} 

  \vspace{0.1in} 
  \section{\centerline{PROFESSIONAL EXPERIENCE}} 
  \vspace{8pt}
     
  {\large \textbf{Akamai Technologies}, Bangalore, India} \hfill   Feb 2019 - Present\\[0.5pt]
  \textbf{Designation} : Senior Solutions Architect \\ \\
  \textbf{Roles and Responsbililties} 
   \begin{itemize} \itemsep -2pt
    \item Working on Customer’s Web Application Architecture and to design and implement a customized solution to maximize their utilization of the Akamai platform.
    \item Working Customer’s Media Delivery(Live and Vod) Architecture. To design and implement a customized solution to deliver live and vod content via the Akamai Platform.
    \item Implementing Security Solutions to Customer’s Application and ensuring that the WebApps are safe and secure.
    \item Implementing DevOps and DevSecOps Solutions for Akamai Customers to help them make use of the Akamai Platform in their DevOps Cycle and increase efficiency.
    \item Deliver training on Akamai products and services to internal Akamai employees, to Akamai customers, and to Akamai consulting partners.
    \item Have written array of Technical Blogs to help customers and internal folks work efficiently with Akamai Products.
  \end{itemize} \vspace{-6pt}
  
  
  \textbf{Project1} ::Salesforce Application for Daily Case Management Tool\hfill      Aug 2019 to May 2020 \\
  \textbf{Role} : Developer \\
  \textbf{Technologies Used}: Jquery,Nodejs,SQL,HTML,CSS
  
   \begin{itemize} \itemsep -2pt
    \item Built an in house tool to log the daily udpates on top of salesforce. 
    \item Played role as Only Developer and Project Manager. 
    \item Tool is very instrumental in increasing the productivity.
    \item Took was widely appreciated by stakeholders since the case status was very accurately known.
  \end{itemize} \vspace{-6pt}

  \textbf{Project2} ::CLI and SDK Development\hfill      May 2020 - \\
  \textbf{Role} : Developer \\
  \textbf{Technologies Used}: Python
  
   \begin{itemize} \itemsep -2pt
    \item Developed the CLIs for Akamai Products like CAC,MediaServices,Datastream,Access Revocation
    \item Built the SDKs for Akamai Products like AkamaiProperty,Datastream and China CDN.
  \end{itemize} \vspace{-6pt}

\hfill   
\noindent\rule{20cm}{0.4pt}

{\large \textbf{Cisco Systems}, Bangalore, India} \hfill        Aug 2016 - Feb 2019 \\[0.5pt]

\textbf{Project1} ::Protocols of Cisco Wireless Lan Controller. \hfill      Aug 2016 to Feb 2019 \\
\textbf{Designation} : Senior Software Engineer \\
\textbf{Role} : Developer \\
\textbf{Technologies Used}: C,Yang,Python,MIBs.

 \begin{itemize} \itemsep -2pt
  \item Have worked on Network Assurance of WLC.
  \item Extensively worked on SNMP module for WLC. Official reviewer of MIBs for the BU.
  \item Involved in sustenance for features like Mobility,CDP and EOGRE.
\end{itemize} \vspace{-6pt}


\textbf{Project2} ::ns3-802.11ax-simulator \hfill      May 2015 to Nov 2015 \\

\textbf{Role} : Developer \\
\textbf{Technologies Used}: C,ns3 Simulator

 \begin{itemize} \itemsep -2pt
  \item Implemented the infra for communication between the modules.
  \item Seperated out the monolithic arhictecture.
  \item Github Link: https://github.com/cisco/ns3-802.11ax-simulator
\end{itemize} \vspace{-6pt}

\textbf{Project3} :Cisco SDN Solution for Protocol Indendent SDN Switches. \hfill      May 2015 to Nov 2015 \\
\textbf{Designation} : Intern \\
\textbf{Role} : Developer \\
\textbf{Technologies Used}: C, C++, Python .

 \begin{itemize} \itemsep -2pt
  \item  Separation of single monolithic structure of the Cisco SDN SDK.
  \item Implementation of P4 Interpretor to the proprietary language used by Cisco SDK.
  \item Dynamic generation of Yang models for the new protocols which will be used to manage the network devices.
\end{itemize} \vspace{-6pt}

\hfill   
\noindent\rule{20cm}{0.4pt}

{\large \textbf{Samsung Research India Bangalore(SRI-B)}, Bangalore, India} \hfill        August 2010 - December 2013 \\[0.5pt]

\textbf{Project1} :AllShare Framework For Tizen Mobile \hfill      Jan 2013 to Dec 2013 \\
\textbf{Designation} : Senior Software Engineer \\
\textbf{Role} : Module lead \\
\textbf{Technologies Used}: Tizen OS, C, C++ .

 \begin{itemize} \itemsep -2pt
  \item  Responsible for AllShare Framework's successful porting into Tizen Mobile.
  \item  Improved the performance of protocol stack by using code optimization techniques.
    \item  Efficiently Handled all high priority issues during the commercialization of Tizen Mobile Phones.
    \item Served as contact point of Tizen DLNA in the organization.
  \item Got the Digital Media Client and Digital Media Server 'DLNA certification' for Tizen Mobile Phone by fixing all CTT issues.
  \item Lead the module of stabilizing the Digital Media Server for Tizen Mobile and fixed all the issues raised during the commercialization.
\end{itemize} \vspace{-6pt}

\textbf{Project2} :AllShare Framework Development for Android mobiles \hfill      Aug 2011 to Dec 2012 \\
\textbf{Designation}: Software Engineer \& Senior Software Engineer\\
\textbf{Role} : Core developer\\
\textbf{Technologies Used}: Android, C, C++ .

 \begin{itemize} \itemsep -2pt
  \item  Implemented Command Prompt User Interface for AllShare applications like Digital Media Server and Digital Media Client.
  \item  Got the Digital Media Client and Digital Media Server 'DLNA certification' for Android Mobile Phones by fixing all CTT issues.
  \item  Implemented various modules like MSCP, MRCP \& Kiescp.
  \item  Implemented Logging mechanisms and ACL feature for entire AllShare framework.
  \item  Handled all the issues efficiently during the successful commercialization of Galaxy S3,S4 and Galaxy Note2.
  \item Responsible for resolving day to day integration issues and ensuring timely and successful integration activities.
\end{itemize} \vspace{-6pt}

AllShare is a UPnP based framework, which provides an easier way to connect and communicate between the smart devices in the home network. Applications written on top of this framework can store, share and enjoy contents securely at your home with your family.

\textbf{Project3} :Commercialization of Samsung Smart TV 2013 \hfill      May 2012 to Nov 2012 \\
\textbf{Designation}: Senior Software Engineer\\
\textbf{Role} : Core Developer\\
\textbf{Technologies Used}: Unix, C, C++ .

 \begin{itemize} \itemsep -2pt
  \item  Fixed all the issues of DLNA module in Samsung Smart TV during the commercialization in South Korea.
  \item  Performed the Inter-Operability test with more than 100 UPnP and DLNA devices and fixed all issues found in TV.
  \item  Did Regression Testing on Tv and fixed issues if any found in a short span.
  \item  Served as Contact point for DLNA TV Project in the organization .
  \item Responsible for resolving day to day integration issues and ensuring timely and successful integration activities.
\end{itemize} \vspace{-6pt}

\textbf{Project4} :DLNA for Refrigerator(Coin) \hfill    Aug 2012 to Sep 2012 \\
\textbf{Designation}: Senior Software Engineer\\
\textbf{Role} : Lead \\
\textbf{Technologies Used}: Windows, C, C++ .

 \begin{itemize} \itemsep -2pt
  \item  Implemented Digital Media Server , Digital Media Renderer for the Refrigerator platform  
  \item  Singly handled the whole module by developing,testing and fixing the issues found.
  \item  Served as Contact point for Coin Project in the organization .
\end{itemize} \vspace{-6pt}

\textbf{Project5} :Commercialization of Samsung Set Top Box \hfill    March 2011 to June 2011 \\
\textbf{Designation}: Software Engineer\\
\textbf{Role} : Developer \\
\textbf{Technologies Used}: Windows, Linux, C, C++ 

 \begin{itemize} \itemsep -2pt
  \item  Implemented Search functionality which was not presented in the Set Top box then. 
  \item  Fixed all the issues of search and browse of DMS.
  \item  Worked for DLNA certification of Samsung Multimedia Platform DMC.
\end{itemize} \vspace{-6pt}


\vspace{0.1in} 
\section{\centerline{ TECHNICAL PROFICIENCY}}
\vspace{10pt} 
\begin{itemize}
\item \textbf{Programming Languages:} Python,C,C++,Javascript.
\item \textbf{Cloud:} AWS,Azure and GCP
\item \textbf{Operating System:} Tizen,Android,Linux,Windows.
\item \textbf{Devops Tools:} Github Actions,Jenkins
\item \textbf{Build and Debugging tools:} Vim,GCC,GDB,Source Insight,Visual Studio,Eclipse,Android NDK,Tizen SDK,Valgrind.
\item \textbf{Version Management:} Github,BitBucket,Gitea
\end{itemize}
 

\vspace{0.1in} 
\section{\centerline{ HOBBY PROJECTS}}
\vspace{10pt} 
\begin{itemize}
\item Fitness Class Auto Booker.
\item Covid Stats Tweeter
\item Cowin Slots Notifier 
\item India News Notifier 
\item Motivational Quotes to Inspire 
\item TTD Notifications 
\item Reality Show Bulk Voter 
\item URL Shortner 
\end{itemize}


\end{resume} 
\end{document}












